Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging

### 2013-03-07 HRUIonGPU/jrnl_article.tex
uffc article

To investigate the image quality of both the Capon and BS Capon beamformer a phantom was simulated using Field II \cite{Jensen1992} (Fig. \ref{fig:phantom}). The simulation was performed using a $\lambda/2$ pitch, 10 $\mu$m kerf, 80\% bandwidth and 10 mm high phased array. The transducer was excited with a 3.4 MHz and $1.5\lambda$ long pulse with transmit focus at 90 mm. The phantom contains two circular areas, one bright at 24 dB and one dark at -30 dB, and two point targets at 40 dB initially located at 90 mm depth. Speckle level is at 0 dB. The resulting image has been processed both using DAS with uniform weights, Capon and BS Capon. The presented image is the first frame in a series of images where motion is imposed on both circles, point targets and the probe. The entire simulation is presented in an attached video.

Fig. \ref{fig:invivo} presents results of applying Capon and BS Capon on an \textit{in-vivo} image of the left ventricle. The image was acquired using an experimental research scanner equipped with a 64 elements and $0.65\lambda$ pitched phased array in harmonic mode (1.7 MHz at transmit and 3.5 MHz at receive). The image is extracted from a cardiac cycle, that can be viewed in its full length in an attached video. It is included to show that Capon beamforming in both element- and beam-space is feasible for cardiac imaging, not just in simulations.

>>>>

To investigate the image quality of both the Capon and BS Capon beamformer a phantom was simulated using Field II \cite{Jensen1992} (Fig. \ref{fig:phantom}). The simulation was performed using a $\lambda/2$ pitch, 10 $\mu$m kerf, 80\% bandwidth and 10 mm high phased array. The transducer was excited with a 3.4 MHz and $1.5\lambda$ long pulse with transmit focus at 90 mm. The phantom contains two circular areas, one bright at 24 dB and one dark at -30 dB, and two point targets at 40 dB initially located at 93 mm depth. Speckle level is at 0 dB, covering an area from $\pm90\degree$ in azimuth. The resulting image has been processed both using DAS with uniform weights, Capon and BS Capon. The presented image is the first frame in a series of images where motion is imposed on both circles, point targets and the probe. The entire simulation is presented in an attached video.

Fig. \ref{fig:invivo} presents results of applying Capon and BS Capon on an \textit{in-vivo} image of the left ventricle. The image was acquired using a 64 elements and $0.65\lambda$ pitched phased array in harmonic mode (1.7 MHz at transmit and 3.5 MHz at receive). The image is extracted from a cardiac cycle, that can be viewed in its full length in an attached video. It is included to show that Capon beamforming in both element- and beam-space is feasible for cardiac imaging, not just in simulations.
